### 2019-05-10 initial/notes.tex
stash

The other timescale of interest is how long it takes $\hat{s}$ to reach a
Cassini State. We may present crude estimates in the $s \gg s_c$ strong
spin-orbit coupling limit; consider starting $\mu = -1 + \delta$, then to
leading order
\begin{align}
    \pd{\delta}{\tau} &\approx +\epsilon \delta,\nonumber\\
    \delta(\epsilon\tau) &\approx \delta_0e^{\epsilon \tau}
\end{align}
Setting $\delta \sim 1$ gives $\tau_{CS} = -\frac{1}{\epsilon}\ln \delta_0$ the
timescale it takes to reach $\mu = 0$ which is of order the timescale to reach
the CS\@. This reinforces our expectation that synchronization is probably no
faster than reaching the Cassini state, but that a significant fraction of
initial conditions below the separatrix should be able to reach a Cassini State
before tides synchronize.

Under this assumption, it would appear that points that start inside the
separatrix (small) stay inside the separatrix, points that start above the
separatrix stay above and undergo resonant obliquity excitation ($\sim 50\%$),
and finally points that start outside the separatrix probably end up at either
CS1 or CS2 probabilistically depending on $\eta(\Delta T(\mu_0))$ where $\Delta
T(\mu_0)$ is the arrival time for a state starting at $\mu_0$.

>>>>

The other timescale of interest is how long it takes $\hat{s}$ to reach a
Cassini State. We may present some crude estimates; note that the Cassini state
is located at $\mu_4 = \frac{\eta \cos I}{1 + \eta \sin I} \approx
\frac{s_c}{s}\cos I$. Thus,
\begin{align*}
    \rd{\mu_4}{(\epsilon \tau)} &= -\frac{s_c}{s^2}\cos I
            \rd{s}{(\epsilon\tau)},\\
        &\approx \frac{s_c}{s}\cos I.
\end{align*}
At the same time, $\rd{\mu}{\p*{\epsilon\sigma}} < \frac{2\Omega_1}{s}$, so in
order for $\mu < \mu_4$ to approach the Cassini state, we need $\Omega_1 \gtrsim
s_c$ by a reasonable margin.
